---
title: "Weight of Fish"
author: "Eliana Martines"
date: "spring 2025"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Perch,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="adjustedR^2")

```

### Best Models
Between the two data tables the H-W model—appears to be the most effective.

### Best Two regressor model
Additionally, the data indicates that the H-W models are the two regression models with the best performance.

## Pike

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Pike,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend = "bottom",main="adjustedR^2")


```


### Best Models
According to the data, the 5-element L1–L2–L3–H–W model is the most effective.

### Best Two regressor model
L1–L3 are the best two regressor models.  In other words, the best two regressor models are not the same as the overall best model.  Consequently, an ANOVA test must be performed in order to properly compare them.

## Roach
```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Roach,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend= "bottomleft",main="adjustedR^2")
```

### Best Models
Model 2, which incorporates L3 and W, appears to be the most successful based on the data.

### Best Two regressor model
The best two-regressor model is also Model 2, which consists of the L3 and W variables.

## Final Summary Statements
As can be seen from the data analysis, Model 2, which incorporates the L3 and W variables, is the best model and best two-regressor model shared by both Perch and Roach.  This consistency implies that model performance for these species is not considerably enhanced by the addition of more predictors.  Since there is no discernible difference in model fit between the more complex and simpler models, an ANOVA test is not necessary to compare them or assess statistical significance.

In contrast, the results for pike show a different pattern. The best overall model for pike is Model 5, which includes all five predictors: L1, L2, L3, H, and W. However, the best two-regressor model is Model 2, which only includes L1 and L3. Since these two models are not the same, it is necessary to run an ANOVA test to determine whether the additional predictors in Model 5 significantly improve the model compared to the simpler Model 2. The resulting p-value from this comparison is 8.679e–10, which is far below the typical significance level of 0.05. This indicates that the improvement in model performance from including all five predictors is statistically significant and not due to random chance. Therefore, for pike, Model 5 provides a significantly better fit than the simpler Model 2.