---
title: "Weight of Fish"
author: "Eliana Martines"
date: "spring 2025"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Perch,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="adjustedR^2")

```

### Best Models
Between the two data tables the H-W model—appears to be the most effective.

### Best Two regressor model
Additionally, the data indicates that the H-W models are the two regression models with the best performance.

## Pike

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Pike,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend = "bottom",main="adjustedR^2")


```


### Best Models
According to the data, the 5-element L1–L2–L3–H–W model is the most effective.

### Best Two regressor model
L1–L3 are the best two regressor models.  In other words, the best two regressor models are not the same as the overall best model.  Consequently, an ANOVA test must be performed in order to properly compare them.

## Roach
```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Roach,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend= "bottomleft",main="adjustedR^2")
```

### Best Models
Model 2, which incorporates L3 and W, appears to be the most successful based on the data.

### Best Two regressor model
The best two-regressor model is also Model 2, which consists of the L3 and W variables.

## Final Summary Statements